An RNN Based Mechanism for File Prefeching\\

### 2019-09-10 master/paper.tex
paper

\title{Path2Vec: An NLP Based Mechanism for File Access Pattern Detection\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

@@

\begin{abstract}
    Many scientific applications spend a large proportion of the execution time to access files. 
    To narrow the increasing gap between computing and I/O performance, several optimization techniques were adopted, 
    such as data prefetching and data layout optimization. However, the effectiveness of these optimization processes heavily 
    depends on the understanding of the I/O behavior. Traditionally, spatial locality and temporal locality
    are mainly considered for data prefetching and scheduling policy. Whereas for some complex workloads, the file access pattern 
    is hard to reveal due to ... 
    We propose Path2Vec, an embedding approach to transform filenames to vectors, thus allowing further analysis of access patterns. 
    To evaluate the effectiveness of this mechanism, we implemented a

\end{abstract}

\begin{IEEEkeywords}

@@

The main contributions of this paper can be summerized as follow.
\begin{itemize}
    \item We propose an approach to embedd the names of files or directories with Skipgram algorithm, 
    mapping file/directory names to vectors, thus providing a quantitative way to analyze relations among files and directories.
    \item For purpose of collecting I/O access history, we implement a trace translator into GlusterFS to monitor and trace specific I/O requests.
    \item Base on the embedding mechanism mentioned above, we build a gated recurrent neural network to catch I/O access pattern and encode it with hidden states of the GRU.
    We combine the hidden states with file vectors to build a file classifier, which dynamically decide whether a file should be cached or purged from the cache.

@@

Since version 3.7, the newly implemented feature \textit{tiring} enables different sotrage types to be used by the same logical volume.
As fig shows, the two types of bricks are classified as \textit{cold} and \textit{hot}. The hot group acts as a cache for the cold group. 
With fine-tuned prefeching and cache replacing policy, large propotion of I/O requests are forwarded to \textit{hot} bricks, thus significantly decreasing access latency.
In this case, we can reframe(\textcolor{red}{EDIT}) caching/prefeching optimization tasks to binary classification problems,
where the objective is to dynamically decide whether a file is \textit{hot} or \textit{cold}.

\subsection{Word Embedding}
The concept word embedding is a set of language models for distributed representations of words in \textit{Natural Language Processing}(NLP), 
aiming at mapping natural words to real number vectors based on context provided by specific corpora.
These mapping mechanisms include neural networks, dimensionality reduction on the word co-occurrence matrix, probabilistic methods etc. \textcolor{blue}{refs}

The most widely utilized model is \textit{skip-gram algorithm}\cite{SkipGram}, 
which trains a neural network to predict whether a word is likely to show up near another.
Given a word vocabulary of size $W$, where a word is identified by $w \in {1,\dots,W}$, 
and a corpus consists of a sequence of words $w_1, \dots, w_T$, the objective of skip-gram algorithm is to maximize the following log probability:
\begin{equation}
\frac{1}{T}\sum_{t=1}^{T}\sum_{-c \leq j \leq c,j \neq 0} \log p(w_{t+j} | w_t),
\end{equation}
Where $w_t$ denotes the target word at position $t$ in the training corpus and $c$ is the size of context window.
A basic definition of $p(w_t+j | w_t)$ is the softmax function:
\begin{equation}
%    p(w_O | w_I) = \frac{\exp{v'_{w_O}^{\top}}{b}
\end{equation}
However, it's generally impractical to calculate softmax function due to the tremendous \textbf{(EDIT)}computational complexity,
as the size of vocabulary may be too large.
To estimate ...

@@

Gated recurrent unit(GRU)\textcolor{blue}{ref} is a gating mechanism in RNNs, 
which is like a long short-term memory(LSTM)\textcolor{blue}{ref} with forget gate but has fewer parameters.
See \textcolor{blue}{fig}

\section{Design}
\subsection{Path Embedding Model}
Since words embedding mechanisms have significantly promoted the performance of plenty of NLP tasks, 
we assume that these methodologies are suitable in analytics and optimizations for posix file systems as well.
\textit{e.g.}, given paths like \textit{/a/b/c/}, \textit{/a/b/d}, we can claim(\textcolor{red}{EDIT}) that \textit{a} and \textit{b},
\textit{b} and \textit{c} are parent-child pairs, while \textit{c} and \textit{d} are a pair of brothers with the same parent \textit{b}.
Or, intuitively, they are logically close to each other in this directory tree. 
This basic relation is analogous to 2-Grams (\textcolor{red}{EDIT}) in natural language models.

@@

\subsection{Access Pattern Analytics with Gated Recurrent Neural Network}
\subsubsection{Data pre-processing}
To collect file access histories, we insert a trace translator into GlusterFS.
So far, we mainly focus on file \textit{open} operation in order to detect when, how and what files does the workload start to access during its lifetime,
attemtpting to reveal its underlying access patterns beyond basic locality. 
As \textbf{fig} illustrated, the components of parameter \textit{path} in each \textit{open} request are transformed to vectors and summed up.\textcolor{red}{edit}

\textcolor{blue}{A figure here}

Finally, a sequence of vectors $\mathbf{x}=(\mathbf{x_1}, \dots, \mathbf{x_T})$ representing access history of size $T$ have been generated.

\subsubsection{GRU-based model building\textcolor{red}{edit}}
In our design, we utilize a single-layer GRU to calculate and update the hidden state, which implicitly represents the access pattern of the target workloads. 
Given dataset $\mathbf{x} = (\mathbf{x}_1,\dots,\mathbf{x}_T)$ representing a sequence of file access history excuted by the target workload, 
we take these vectors as input sequence for the GRU and train the model.

At time $t$, the activation $h_t^{(j)}$, which denotes the $j$th element of the hidden state $\mathbf{h}_t$, is a linear interpolation between the previous activation $h_{t-1}^{(j)}$ and the candidate activation $\tilde{h}_t^{(j)}$:
\begin{equation}
    h_t^{(j)} = (1-z_t^{(j)}) h_{t-1}^{(j)} + z_t^{(j)}\tilde{h}_t^{(j)},
\end{equation}
Where $z_t$ is denoted as an \textit{update gate}, calculated by a sigmoid function over input $\mathbf{x_t}$ and previous state $\mathbf{h_{t-1}}$:
\begin{equation}
z_t^{(j)} = \sigma(W_z \mathbf{x}_t + U_z \mathbf{h}_{t-1})^{(j)}
\end{equation}
The candidate acitivation $\tilde{h}_t^{(j)}$ is computed by:
\begin{equation}
    \tilde{h}_t^{(j)} = \tanh(W \mathbf{x}_t + U (\mathbf{r}_t \odot \mathbf{h}_{t-1}))^{(j)}
\end{equation}
Where $\mathbf{r}_t$ are \textit{reset gates} and $\odot$ is a pointwise multiplication(Hadarmard product).
The reset gate is calculated by
\begin{equation}
    r_t^{(j)} = \sigma(W_r \mathbf{x}_t + \mathbf{U}_r \mathbf{h}_{t-1})^{(j)}
\end{equation}
For purpose of discriminating files between \textit{hot} and \textit{cold}, 
our goal is to train the GRU to provide appropriate hidden states for classification. 
We denote $N$ as the approximation of the number of files fit in the cache,
thus at time $t$, the following $N$ files(vectors) are labeled as \textit{hot}, i.e., positive samples, 
while the others are labeled as \textit{cold}(negative).
As long as $\mathbf{h}_t$ is calculated, the objective is to maximize the log probability
\begin{equation}
    \label{eq.obj}
    \sum_{i=1}^N \log P(\mathbf{x}_{t+j}|\mathbf{h}_t)
\end{equation}
Where we calculate the probability $P(\mathbf{x}_{t+j}|\mathbf{h}_t)$ by
\begin{equation}
    P(\mathbf{x}_{t+j}|\mathbf{h}_t) = \sigma(\mathbf{x}^\top_t \mathbf{h}_t)
\end{equation}
Thus we obtain the loss function for training
\begin{equation}
    arg\,max L(\theta) = \sum_{i=1}^N \log \sigma(\mathbf{x}^\top_t \mathbf{h}_t)
\end{equation}
Where the parameter $\theta = \{W_z, U_z, W, U, W_r, U_r\}$.
We train this GRU with BPTT(backpropagation through time)\textcolor{red}{ref}.

\section{Evaluation}
\subsection{Experiment and Parameter Settings}
We choose compiling workloads for experiments and collect a few different repositories from Github,
including \textcolor{red}{edit} files and occupying volume of \textcolor{red}{edit} gigabytes in total.
We split these repositories into two groups, 10 arbitrary repositories for training and the others for testing.

To evaluate the performance of our model,

\subsection{Results}

%\subsection{\textcolor{red}{EDIT}Similarity Experiment for Directory/File Names}
%In this part, we picked up \textcolor{red}{edit} most frequently occured names from vocabulary, which is generated from the training group of repositories with Skip-gram algorithm.
%We utilize PCA(\textit{Principal Component Analysis}) to project these \textcolor{red}{edit} vectors(\textcolor{red}{EDIT}) into a 2-D graph.
%As fig(\textbf{refhere}) illustrates,

@@

There are several works to accomplish in the future. First, the model should be deployed in tiering translator in GlusterFS,
thus making it possible to exploit our model in real fils system for optimization purpose. 
Also, our work should be scaled to more real world workloads rather than compiling.
\bibliographystyle{plain}
\bibliography{paper}

>>>>

\title{An RNN Based Mechanism for File Prefeching\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Hui Chen}
\IEEEauthorblockA{\textit{National University of Defense Technology} \\
Changsha, China\\
code2hack4ever@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{th} Enqiang Zhou*}
\IEEEauthorblockA{\textit{National University of Defense Technology} \\
%\textit{name of organization (of Aff.)}\\
Changsha, China\\
eqzhou@nudt.edu.cn}
}

@@

\begin{abstract}
    Many applications spend a large proportion of the execution time to access files.
    To narrow the increasing gap between computing and I/O performance, several optimization techniques were adopted, 
    such as data prefetching and data layout optimization. However, the effectiveness of these optimization processes heavily 
    depends on the understanding of the I/O behavior. Traditionally, spatial locality and temporal locality
    are mainly considered for data prefetching and scheduling policy. Whereas for most real world workloads, the file access pattern 
    is hard to capture.

    For the goal of deeply and intelligently understanding the I/O access pattern of modern applications, and efficiently optimizing performance of current file systems,
    we propose a new mechanism to embed file names to vectors, and train a gated recurrent neural network to provide policies for file prefeching and cache replacing.
\end{abstract}

\begin{IEEEkeywords}
    \textit{Distributed File System; File Prefetching; Word Embedding; RNN}

@@

The main contributions of this paper can be summerized as follow.
\begin{itemize}
    \item We propose an approach to embed the names of files or directories with Skipgram algorithm, 
    mapping file/directory names to vectors, thus providing a quantitative way to analyze relations among files and directories.
    \item For purpose of collecting I/O access history, we implement a trace translator into GlusterFS to monitor and trace specific I/O requests.
    \item Base on the embedding mechanism mentioned above, we build a gated recurrent neural network to capture I/O access pattern and encode it with hidden states of the GRU.
    We combine the hidden states with file vectors to build a file classifier, which dynamically decide whether a file should be cached or purged from the cache.

@@

Since version 3.7, the newly implemented feature \textit{tiring} enables different sotrage types to be used by the same logical volume.
As Fig.\ref{fig:tiering} shows, the two types of bricks are classified as \textit{cold} and \textit{hot}. The hot group acts as a cache for the cold group. 
With fine-tuned prefeching and cache replacing policy, large propotion of I/O requests are forwarded to \textit{hot} bricks, thus significantly decreasing access latency.
In this case, we can reframe caching/prefeching optimization tasks to binary classification problems,
the objective of which is to dynamically decide whether a file is \textit{hot} or \textit{cold}.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/tiering}
\caption{Data tiering in GlusterFS}
\label{fig:tiering}
\end{figure}

\subsection{Word Embedding}
The concept word embedding is a set of language models for distributed representations of words in \textit{Natural Language Processing}(NLP), 
aiming at mapping natural words to real number vectors based on context provided by specific corpora.
These mapping mechanisms include neural networks, dimensionality reduction on the word co-occurrence matrix, probabilistic methods, etc.

Among the mechanisms metioned above, the Skip-gram model is an efﬁcient method for learning high-quality distributed vector representations that capture a large number of precise syntactic and semantic word relationships.

%Given a word vocabulary of size $W$, where a word is identified by $w \in {1,\dots,W}$, 
%and a corpus consists of a sequence of words $w_1, \dots, w_T$, the objective of skip-gram algorithm is to maximize the following log probability:
%\begin{equation}
%\frac{1}{T}\sum_{t=1}^{T}\sum_{-c \leq j \leq c,j \neq 0} \log p(w_{t+j} | w_t),
%\end{equation}
%Where $w_t$ denotes the target word at position $t$ in the training corpus and $c$ is the size of context window.
%A basic definition of $p(w_t+j | w_t)$ is the softmax function:
%\begin{equation}
%    p(w_O | w_I) = \frac{ \exp( {v'}_{w_O}^{\top} v_{w_I}) }{\sum_{w=1}^W \exp({v'}_w^{\top} v_{w_I})}
%\end{equation}
%However, it's generally impractical to calculate softmax function due to the tremendous \textbf{(EDIT)}computational complexity,
%as the size of vocabulary may be too large.
%To estimate ...

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{images/GRU}
\caption{Gated recurrent unit}
\end{figure}
The GRU(gated recurrent unit)\cite{GRU} is a gating mechanism in RNNs, 
which is like a LSTM(long short-term memory)\cite{LSTM} with forget gate but has fewer parameters.

\section{Design}
\subsection{Path Embedding Model}
Since words embedding mechanisms have significantly promoted the performance of plenty of NLP tasks, 
we assume that these methodologies are suitable in analytics and optimizations for posix file systems as well.
\textit{e.g.}, given paths like \textit{/a/b/c/}, \textit{/a/b/d}, we can claim that \textit{a} and \textit{b},
\textit{b} and \textit{c} are parent-child pairs, while \textit{c} and \textit{d} are a pair of brothers with the same parent \textit{b}.
Or, intuitively, they are logically close to each other in this directory tree. 
This basic relation is analogous to 2-Grams model in natural language models.

@@

\subsection{Access Pattern Analytics with Gated Recurrent Neural Network}
\subsubsection{Data Pre-processing}
To collect file access histories, we insert a trace translator into GlusterFS.
So far, we mainly focus on file \textit{open} operation in order to detect when, how and what files does the workload start to access during its lifetime,
attemtpting to reveal its underlying access patterns beyond basic locality. 
The components of the \textit{path} in each \textit{open} request are transformed and added up to form a vector.
e.g., given $i$th accessed path named \textit{/foo/bar/file}, the three components are respectively transformed to three vectors: $\{\mathbf{v}_1, \mathbf{v}_2, \mathbf{v}_3\}$,
and summed up to form a vector $\mathbf{x}_i = \mathbf{v}_1 + \mathbf{v}_2 + \mathbf{v}_3$.
Finally, a sequence of vectors $\mathbf{x}=(\mathbf{x_1}, \dots, \mathbf{x_T})$ representing access history of size $T$ are generated.

\subsubsection{GRU-based Model Building}
In our design, we utilize a single-layer GRU to calculate and update the hidden state, which implicitly represents the access pattern of the target workloads. 
Given dataset $\mathbf{x} = (\mathbf{x}_1,\dots,\mathbf{x}_T)$ representing a sequence of file access history excuted by the target workload, 
we take these vectors as input sequence for the GRU and train the model.

At time $t$, the activation $h_t^{(j)}$, which denotes the $j$th element of the hidden state $\mathbf{h}_t$, is a linear interpolation between the previous activation $h_{t-1}^{(j)}$ and the candidate activation $\tilde{h}_t^{(j)}$:
\begin{equation}
    h_t^{(j)} = (1-z_t^{(j)}) h_{t-1}^{(j)} + z_t^{(j)}\tilde{h}_t^{(j)},
\end{equation}
Where $z_t$ is denoted as an \textit{update gate}, calculated by a sigmoid function over input $\mathbf{x_t}$ and previous state $\mathbf{h_{t-1}}$:
\begin{equation}
z_t^{(j)} = \sigma(W_z \mathbf{x}_t + U_z \mathbf{h}_{t-1})^{(j)}
\end{equation}
The candidate acitivation $\tilde{h}_t^{(j)}$ is computed by:
\begin{equation}
    \tilde{h}_t^{(j)} = \tanh(W \mathbf{x}_t + U (\mathbf{r}_t \odot \mathbf{h}_{t-1}))^{(j)}
\end{equation}
Where $\mathbf{r}_t$ are \textit{reset gates} and $\odot$ is a pointwise multiplication(Hadarmard product).
The reset gate is calculated by
\begin{equation}
    r_t^{(j)} = \sigma(W_r \mathbf{x}_t + \mathbf{U}_r \mathbf{h}_{t-1})^{(j)}
\end{equation}
For purpose of discriminating files between \textit{hot} and \textit{cold}, 
our goal is to train the GRU to provide appropriate hidden states for classification. 
We denote $N$ as the approximation of the number of files fit in the cache,
thus at time $t$, the following $N$ files(vectors) are labeled as \textit{hot}, i.e., positive samples, 
while the others are labeled as \textit{cold}(negative).
As long as $\mathbf{h}_t$ is calculated, the objective is to maximize the log probability
\begin{equation}
    \label{eq.obj}
    \sum_{i=1}^N \log P(\mathbf{x}_{t+j}|\mathbf{h}_t)
\end{equation}
Where we calculate the probability $P(\mathbf{x}_{t+j}|\mathbf{h}_t)$ by
\begin{equation}
    P(\mathbf{x}_{t+j}|\mathbf{h}_t) = \sigma(\mathbf{x}^\top_t \mathbf{h}_t)
\end{equation}
Thus we obtain the loss function for training
\begin{equation}
    arg\,max L(\theta) = \sum_{i=1}^N \log \sigma(\mathbf{x}^\top_t \mathbf{h}_t)
\end{equation}
Where the parameter $\theta = \{W_z, U_z, W, U, W_r, U_r\}$.
We train this GRU with BPTT(backpropagation through time).

\section{Evaluation}
\subsection{Experiment and Parameter Settings}
We use a 4 node cluster to build a distributed file system based on GlusterFS. 
Each node is deployed on a CentOS7 Server virtual machine on the different physical machines connected by Ethernet, 
and each virtual machine has one CPU, 1G memory and 20G RAM. Each node is equiped with one hard disk as \textit{cold} brick,
and an SSD driver with volume of 40 GB deployed as the \textit{hot} brick.

We choose compiling workloads as the target, and collect 20 different repositories from Github.
%including \textcolor{red}{edit} files and occupying volume of \textcolor{red}{edit} gigabytes in total.
We split these repositories into two groups, 10 arbitrary repositories for training and the others for testing.

To evlatuate the performance of our model, we adjust the context window size $N$ for testing. 
Whereas another hyper parameter, the dimension of the embedded vectors is fixed to be 16. 
\subsection{Results for Hit Rate and Access Latency Testing}

\begin{table}[htbp]
    \caption{Results for hit rate and access latency testing} 
\begin{center}
    \begin{tabular}{ |c|c|c| } 
     \hline
     \textbf{\textit{Size of}}&\textbf{\textit{Average}} &\textbf{\textit{Average Access}}\\ 
     \textbf{\textit{Context Window}}& \textbf{\textit{Hit Rate}} & \textbf{\textit{Latency(ms)}}\\
     \hline
     \hline
     0	&0	&270\\
     \hline
     50	&0.13	&263\\
     \hline
     100	&0.21	&255\\
     \hline
     150	&0.26	&242\\
     \hline
     200	&0.42	&233\\
     \hline
     250	&0.53	&225\\
     \hline
     300	&0.66	&221\\
     \hline
     350	&0.77	&207\\
     \hline
     400	&0.74	&218\\
     \hline
     450	&0.7	&231\\
     \hline
     500	&0.67	&245\\
     \hline
    \end{tabular}
\end{center}

%    The first line of data refer to the baseline, where the size of context window is set to 0, 
%    that means our prefetching mechanism does not work.}
    \label{table:result}
\end{table}
As shown in Table. \ref{table:result}, where the first line of data refers to the baseline, i.e., the model and the prefeching mechanism do not work.
We can conclude that our mechanism bring benifits to the file system compared to no-prefeching state.
From Fig.~\ref{fig:hit_rate} and Fig.~\ref{fig:latency}, we can clearly observe that this profit brought by our mechanism is limited, 
due to the increasing tradeoff when the context window is enlarging.
\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{images/hit_rate}
\caption{Hit rate testing}
\label{fig:hit_rate}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{images/latency}
\caption{Access latency testing}
\label{fig:latency}
\end{figure}
%\subsection{\textcolor{red}{EDIT}Similarity Experiment for Directory/File Names}
%In this part, we picked up \textcolor{red}{edit} most frequently occured names from vocabulary, which is generated from the training group of repositories with Skip-gram algorithm.
%We utilize PCA(\textit{Principal Component Analysis}) to project these \textcolor{red}{edit} vectors(\textcolor{red}{EDIT}) into a 2-D graph.
%As fig(\textbf{refhere}) illustrates,

@@

There are several works to accomplish in the future. First, the size of context window should be adaptive to the volume of the cache, 
as well as the CPU resources of the storage nodes.
Also, our work should be scaled to serve more real world workloads rather than single process applications like compiling, 
especially for scientific workloads in exscale parallel computing and cloud computing circumstances.
\bibliographystyle{plain}
\bibliography{paper}
